Yoghurt under stress

### 2014-06-16 seminaire_Tanakalab.tex
Primary creep is kinetically reversible

\tikzset{external/force remake}
\begin{frame}{Primary creep}
\begin{columns}
\column{0.55\textwidth}
\begin{tikzpicture}
\begin{loglogaxis}[
	width=\textwidth,
	height=0.8\textwidth,
	xmin=2e-2, xmax=4e5, xlabel={time (\si{\second})},
	ylabel={Strain rate $\dot{\gamma}$ (\si{\per\second})},
	cycle list name=earthy,
	no marks,
	]
	\addplot table[y index=2]{Y27_200Pa_gdot_decimated.txt} node (s200){};
	\addplot table[y index=2]{Y38_300Pa_gdot_decimated.txt} node (s300){};
	\addplot table[y index=2]{Y25_400Pa_gdot_decimated.txt}  node (s400){};
	\addplot table[y index=2]{Y32_550Pa_gdot_decimated.txt}  node (s550){};
	\addplot table[y index=2]{Y39_1000Pa_gdot_decimated.txt} node (s1000){};
	\addplot[Accent2, ultra thick, domain={0.1:1e3}] {0.01*x^(-0.85)} node[pos=0.75, below left] {$\dot{\gamma}(t)\sim t^{-0.85}$};
\end{loglogaxis}
\end{tikzpicture}

@@

>>>>

%\tikzset{external/force remake}
\begin{frame}{Primary creep}
\begin{columns}
\column{0.55\textwidth}
\begin{tikzpicture}
\begin{loglogaxis}[
	width=\textwidth,
	height=0.8\textwidth,
	xmin=2e-2, xmax=4e5, xlabel={time (\si{\second})},
	ylabel={Strain rate $\dot{\gamma}$ (\si{\per\second})},
	cycle list name=earthy,
	no marks,
	]
	\addplot table[y index=2]{Y27_200Pa_gdot_decimated.txt} node (s200){};
	\addplot table[y index=2]{Y38_300Pa_gdot_decimated.txt} node (s300){};
	\addplot table[y index=2]{Y25_400Pa_gdot_decimated.txt}  node (s400){};
	\addplot table[y index=2]{Y32_550Pa_gdot_decimated.txt}  node (s550){};
	\addplot table[y index=2]{Y39_1000Pa_gdot_decimated.txt} node (s1000){};
	\addplot[Accent2, ultra thick, domain={0.1:1e3}] {0.01*x^(-0.85)} node[pos=0.75, below left] {$\dot{\gamma}(t)\sim t^{-0.85}$};
\end{loglogaxis}
\end{tikzpicture}

@@

\tikzset{external/force remake}
\begin{frame}{Primary creep}
\begin{block}{Local insight from \movie[externalviewer]{ultrasounds}{Yaourt110_primary.avi}}
\begin{itemize}
	\item homogeneous \movie[externalviewer]{strain field}{Yaourt110_profils.avi} (no wall slip, no shear band)
	\item if present, plastic events are below our resolution (a few \si{\micro\metre})
\end{itemize}
\end{block}

\begin{block}{Partial creep and recovery}
\begin{tikzpicture}
\begin{axis}[
	width=\textwidth,
	height=8\baselineskip,
	xlabel={time (\si{\second})},
	ylabel={strain $\gamma$},
	xmin=-1e3, xmax=2.8e4,
	]
	\addplot[black, no marks] table {Y261_oscil_creep_recovery_100Pa_decimated.txt};
	\begin{scope}[<-,Main, inner sep=0]
	\draw (axis cs:0,0) -- +(1em,0) node[anchor=west]{$\sigma\leftarrow \SI{100}{\pascal}$};
	\draw (axis cs:600,0.2727007) -- +(1em,0) node[anchor=west]{$\sigma\leftarrow 0$};
	\draw (axis cs:8600,0.0159) -- +(0,1em) node[anchor=base east]{$\gamma\leftarrow 0$};
	\end{scope}
\end{axis}
\end{tikzpicture}
\end{block}

$\Rightarrow$ Primary creep is ``kinetically'' reversible (no detectable structure damage, but viscous dissipation)

\end{frame}
\tikzset{external/force remake=false}
